### 2025-05-16 appendices/haiti/appendixHaiti.tex
Adressing pre-defense review issue: Table B.2 exceeds past the 1" right side margin
Fixing pre-defense review: "All figure and table captions must match word for word up to the first punctuation mark."

\begin{figure}[ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/m1Profs-1} 
\end{knitrout}
\caption[MCAP confidence intervals for Model 1 parameters.]{\label{fig:m1Profs}MCAP confidence intervals for Model 1 parameters. The vertical blue line indicates the smoothed MLE.}
\end{figure}

\begin{table}[!h]
\centering
\caption[Model~1 parameter estimates and confidence intervals.]{\label{tab:mod1CI}Model~1 parameter estimates and their corresponding confidence intervals, obtained via the MCAP algorithm.}
\vspace{2mm}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval}
\\
\hline
\hline

@@

  Process noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{Epi}$ & $0.092$
   &
  $(0.085, 0.113)$
\\
\hline

  Process noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{End}$ & $0.118$
   &
  $(0.092, 0.179)$
\\
\hline

@@

\begin{figure}[ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/m2Profs-1} 
\end{knitrout}
\caption[MCAP confidence intervals for Model 2 parameters.]{\label{fig:m2Profs}MCAP confidence intervals for Model 2 parameters. The vertical blue line indicates the MLE.}
\end{figure}

\begin{table}[!h]
\centering
\caption[Model~2 parameter estimates and confidence intervals.]{\label{tab:mod2CI}Model~2 parameter estimates and their corresponding confidence intervals, obtained via profile likelihood.}
\vspace{2mm}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval}
\\
\hline
\hline

@@

\begin{figure}[ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/m3Profs-1} 
\end{knitrout}
\caption[MCAP confidence intervals for Model 3 parameters.]{\label{fig:m3Profs}MCAP confidence intervals for Model 3 parameters. The vertical blue line indicates the smoothed MLE.}
\end{figure}

\begin{table}[!h]
\centering
\caption[Model~3 parameter estimates and confidence intervals.]{\label{tab:mod3CI}Model~3 parameter estimates and their corresponding confidence intervals, obtained via the MCAP algorithm.}
\vspace{2mm}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval}
\\
\hline
\hline

 Process Noise {\small (wk\textsuperscript{1/2})} & $\sigmaProc$ & $0.218$
   &
  $(0.203, 0.230)$
\\
\hline

 Water Survival {\small (wk)} & $\Wremoval^{-1}$ & $0.108$
   &
  $(0.087, 0.110)$
\\
\hline

 Human to Water Shedding {\small $\frac{\mathrm{km^2}}{\mathrm{wk}}$} & $\Wshed$ & $\ensuremath{9.77\times 10^{-7}}$
   &
  $(\ensuremath{8.64\times 10^{-7}}, \ensuremath{1.25\times 10^{-6}})$
\\
\hline

@@

\end{knitrout}
\caption[Replicating Model 1 epidemic phase parameter distributions]{\label{fig:PlotEpiDist}
Bivariate distributions of parameter estimates after fitting epidemic phase of the Model~1 following the procedure described by \citet{lee20}. Compare to Figure S8 in the supplement of \citet{lee20}.
}
\end{figure}

@@

\end{knitrout}
\caption[Replicating Model 1 endemic phase parameter distributions]{\label{fig:plotEndParams}
Bivariate distributions of parameter estimates after fitting endemic phase of the Model~1 following the procedure described by \citet{lee20}. Compare to Figure~S9 in the supplement of \citet{lee20}.
}
\end{figure}

\begin{figure}[!h]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/plotMod1Sims-1} 
\end{knitrout}
\caption[Simulations from replicated Model 1]{\label{fig:plotMod1Sims}
Simulations from Model~1 using parameter sets that were generated by running source code provided by \citet{lee20}. Compare to Figure~S7 in the supplement of \citet{lee20}. The upper bound for the likelihood of this model is -3031.
}
\end{figure}

@@

\begin{figure}[!h]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/plotModel2Rep-1} 
\end{knitrout}
\caption[Model~2 trajectories.]{\label{fig:mod2rep}
Model 2 trajectories using the \code{haitipkg}. Compare to Figure S15 in the supplement of \citet{lee20}.
}
\end{figure}

@@

\begin{figure}[!h]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/PlotMod3Rep-1} 
\end{knitrout}
\caption[Simulations from replicated Model 3]{\label{fig:mod3rep}
Simulations from Model~3.
Compare to Figure S18 in the supplement of \citet{lee20}.
}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/h3UnitLikes-1} 
\end{knitrout}
\caption[Model~3 unit log-likelihoods.]{\label{fig:h3UnitLikes}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model prior to the inclusion of parameters that account for Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/CondLLFig-1} 
\end{knitrout}
\caption[Conditional log-likelihoods without hurricane adjustment]{\label{fig:condLL}Conditional log-likelihoods of Model~3 prior to the inclusion of the Hurricane Matthew related parameters.}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/finalCondLLFig-1} 
\end{knitrout}
\caption[Conditional log-likelihoods with hurricane adjustment]{\label{fig:finalCondLL}Conditional log-likelihoods of Model~3 after adding and estimating the parameters related to Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/finalUnitLLFig-1} 
\end{knitrout}
\caption{\label{fig:finalUnitLL}Log-likelihoods of Model~3 for each department compared to the corresponding benchmark model after adding and estimating parameters related to Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/h3SusFig-1} 
\end{knitrout}
\caption[Estimated susceptible population over time.]{\label{fig:h3Sus}Percentage of individuals that are in the susceptible compartment.
Simulations from Model~3 under initial conditions are displayed in red; simulations from the filtering distribution of model are displayed in blue.
The dashed line represents the end of the observed data.}
\end{figure}

>>>>

\begin{figure}[ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/m1Profs-1}

\end{knitrout}
\caption[MCAP confidence intervals for Model 1 parameters.]{\label{fig:m1Profs}MCAP confidence intervals for Model 1 parameters. The vertical blue line indicates the smoothed MLE.}
\end{figure}

\begin{table}[!h]
\centering
\caption[Model~1 parameter estimates and corresponding confidence intervals.]{\label{tab:mod1CI}Model~1 parameter estimates and corresponding confidence intervals. Confidence intervals were obtained via the MCAP algorithm.}
\vspace{2mm}
\begin{tabular}{|L{3.60cm}|C{2.1cm}|C{1.9cm}|C{3.95cm}|}
\hline
\centering \textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval} \\
\hline
\hline

@@

  Process noise {\footnotesize (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{Epi}$ & $0.092$
   &
  $(0.085, 0.113)$
\\
\hline

  Process noise {\footnotesize (wk\textsuperscript{1/2})} & $\sigmaProc: \mathrm{End}$ & $0.118$
   &
  $(0.092, 0.179)$
\\
\hline

@@

\begin{figure}[ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/m2Profs-1}

\end{knitrout}
\caption[MCAP confidence intervals for Model 2 parameters.]{\label{fig:m2Profs}MCAP confidence intervals for Model 2 parameters. The vertical blue line indicates the MLE.}
\end{figure}

\begin{table}[!h]
\centering
\caption[Model~2 parameter estimates and corresponding confidence intervals.]{\label{tab:mod2CI}
Model~2 parameter estimates and corresponding confidence intervals. Confidence intervals were obtained via profile likelihood.}
\vspace{2mm}
\begin{tabular}{|L{3.25cm}|C{2.1cm}|C{1.9cm}|C{4.2cm}|}
\hline
\centering \textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval} \\
\hline
\hline

@@

\begin{figure}[ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/m3Profs-1}

\end{knitrout}
\caption[MCAP confidence intervals for Model 3 parameters.]{\label{fig:m3Profs}MCAP confidence intervals for Model 3 parameters. The vertical blue line indicates the smoothed MLE.}
\end{figure}

\begin{table}[!h]
\centering
\caption[Model~3 parameter estimates and corresponding confidence intervals.]{\label{tab:mod3CI}Model~3 parameter estimates and corresponding confidence intervals. Confidence intervals were obtained via the MCAP algorithm.}
\vspace{2mm}
\begin{tabular}{|L{3.60cm}|C{2.1cm}|C{1.9cm}|C{4.3cm}|}
\hline
\centering \textbf{Mechanism} & \textbf{Parameter} & \textbf{MLE} & $\bm{95\%}$ \textbf{Confidence Interval} \\
\hline
\hline

 Process Noise {\footnotesize (wk\textsuperscript{1/2})} & $\sigmaProc$ & $0.218$
   &
  $(0.203, 0.230)$
\\
\hline

 Water Survival {\footnotesize (wk)} & $\Wremoval^{-1}$ & $0.108$
   &
  $(0.087, 0.110)$
\\
\hline

 Human to Water Shedding {\footnotesize $\frac{\mathrm{km^2}}{\mathrm{wk}}$} & $\Wshed$ & $\ensuremath{9.77\times 10^{-7}}$
   &
  $(\ensuremath{8.64\times 10^{-7}}, \ensuremath{1.25\times 10^{-6}})$
\\
\hline

@@

\end{knitrout}
\caption[Replicating Model 1 epidemic phase parameter distributions.]{\label{fig:PlotEpiDist}
Replicating Model 1 epidemic phase parameter distributions. Distributions of parameter estimates after fitting epidemic phase of the Model~1 following the procedure described by \citet{lee20}. Compare to Figure S8 in the supplement of \citet{lee20}.
}
\end{figure}

@@

\end{knitrout}
\caption[Replicating Model 1 endemic phase parameter distributions.]{\label{fig:plotEndParams}
Replicating Model 1 endemic phase parameter distributions. Distributions of parameter estimates after fitting endemic phase of the Model~1 following the procedure described by \citet{lee20}. Compare to Figure~S9 in the supplement of \citet{lee20}.
}
\end{figure}

\begin{figure}[!h]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/plotMod1Sims-1} 
\end{knitrout}
\caption[Simulations from replicated Model 1.]{\label{fig:plotMod1Sims}
Simulations from replicated Model 1. Parameter sets were generated by running source code provided by \citet{lee20}. Compare to Figure~S7 in the supplement of \citet{lee20}. The upper bound for the likelihood of this model is -3031.
}
\end{figure}

@@

\begin{figure}[!h]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/plotModel2Rep-1} 
\end{knitrout}
\caption[Replicated Model~2 trajectories.]{\label{fig:mod2rep}
Replicated Model~2 trajectories. The original model was re implemented using the \code{haitipkg}. Compare to Figure S15 in the supplement of \citet{lee20}.
}
\end{figure}

@@

\begin{figure}[!h]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/PlotMod3Rep-1} 
\end{knitrout}
\caption[Simulations from replicated Model 3.]{\label{fig:mod3rep}
Simulations from replicated Model~3.
Compare to Figure S18 in the supplement of \citet{lee20}.
}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/h3UnitLikes-1}

\end{knitrout}
\caption[Model~3 unit log-likelihoods.]{\label{fig:h3UnitLikes}Model~3 unit log-likelihoods. Values for each department are compared to the corresponding benchmark model prior to the inclusion of parameters that account for Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/CondLLFig-1} 
\end{knitrout}
\caption[Conditional log-likelihoods of Model~3 without Hurricane Matthew adjustment.]{\label{fig:condLL}Conditional log-likelihoods of Model~3 without Hurricane Matthew adjustment.}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/finalCondLLFig-1} 
\end{knitrout}
\caption[Conditional log-likelihoods of Model~3 with Hurricane Matthew adjustment.]{\label{fig:finalCondLL}Conditional log-likelihoods of Model~3 with Hurricane Matthew adjustment.}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=\maxwidth]{figure/finalUnitLLFig-1}

\end{knitrout}
\caption[Model~3 unit log-likelihoods after hurricane adjustment.]{\label{fig:finalUnitLL}Model~3 unit log-likelihoods after hurricane adjustment. Values for each department are compared to the corresponding benchmark model after the inclusion of parameters that account for Hurricane Matthew.}
\end{figure}

@@

\begin{figure}[!ht]
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\maxwidth]{figure/h3SusFig-1} 
\end{knitrout}
\caption[Estimated susceptible population over time.]{\label{fig:h3Sus}Estimated susceptible population over time.
Simulations from Model~3 under initial conditions are displayed in red; simulations from the filtering distribution of model are displayed in blue.
The dashed line represents the end of the observed data.}
\end{figure}

### 2025-05-16 chapters/arima2/arima2.Rnw
Fixing pre-defense review: "All figure and table captions must match word for word up to the first punctuation mark."

\begin{figure}[ht]
<<mutliMode-fig, fig.height=3.5, fig.width=7>>=
ggpubr::ggarrange(
  plotlist = ggs,
  legend = 'right',
  common.legend = TRUE
)
@
\caption[Multi-node MA(1) models]{\label{fig:multiMode}The profile log-likelihood of data simulated from four distinct MA(1) models, demonstrating a few examples of multimodal likelihood surfaces. The solid, black line indicates the true value of $\theta_1$; the dotted line is the CSS-initialization. The dashed lines correspond to the estimate $\hat{\theta}_1$ using \code{stats:arima} (red) and our proposed algorithm (implemented in \code{arima2::arima}, blue).}
\end{figure}

@@

\begin{figure}[!ht]
<<simProps, fig.height=3, fig.width=4.5>>=
wide_res %>%
  filter(P != 0 & Q !=0) %>%
  group_by(P, Q, n) %>%
  summarize(pct_improve = sum(ll_arima2 > ll_arima, na.rm = TRUE) / n()) %>%
  ggplot(aes(x = n, y = pct_improve)) +
  facet_grid(Q~P, labeller = labeller(P = AR_labs, Q = MA_labs)) +
  geom_line() +
  geom_point() +
  scale_y_continuous(limits = c(0, 0.6)) +
  ylab("Proportion of Improved Fits") +
  xlab("Number of observations (n)")
@
\caption[Proportion of improved models]{\label{fig:simProps}Proportion of simulated data with improved likelihood from using multiple restarts (Algorithm~\ref{alg:mle}).}
\end{figure}

@@

ggpubr::ggarrange(
  gg_fisher, gg_profile, align = 'h', nrow = 1,
  labels = 'AUTO',
  label.x = c(0.16, 0)
)
@
\caption[Confidence interval coverage]{\label{fig:pctCovered}Proportion of models that achieved nominal coverage of Bonferroni adjusted $95\%$ confidence intervals. The dashed line denotes the target coverage level. (A) Confidence intervals created using Fisher's information matrix. (B) Confidence intervals created using profile likelihoods.}
\end{figure}

@@

simTables %>%
  group_by(n, P, Q, max_repeat) %>%
  summarize(
    pct_consistent = sum(consistent, na.rm = TRUE) / sum(!is.na(consistent))
  ) %>%
  ggplot(
    aes(
      x = n, y = pct_consistent,
      group = as.factor(max_repeat),
      color = as.factor(max_repeat),
      linetype = as.factor(max_repeat)
    )
  ) +
  geom_line() +
  geom_point() +
  facet_grid(P~Q, labeller = labeller(P = AR_labs, Q = MA_labs)) +
  ylab("Proportion of Tables\n that are Consistent") +
  xlab("Number of observations") +
  theme(legend.title = element_blank(), legend.position = 'bottom') +
  scale_color_discrete(labels = restart_labels) +
  scale_linetype_discrete(labels = restart_labels) +
  scale_y_continuous(limits = c(0.35, 1))
@
\caption[AIC table improvements]{\label{fig:AICtabRes}Data is generated from ARMA$(p, q)$ models with $(p, q) \in \{1, 2, 3\}^2$, and the corresponding AIC table is created. The Y-axis shows the percentage of tables that were consistent. M is the number of times a maxima is observed before the algorithm terminates, so $M=1$ corresponds to the standard maximization procedure.}
\end{figure}

@@

    \caption[AIC values of ARMA model for Lake Michigan-Huron]{\label{tab:huronTab}AIC values for an ARMA(p, q) model fit to Lake Michigan-Huron depths. Table~\ref{tab:AIC1} was computing using only a single parameter initialization. Table~\ref{tab:AIC2} was computed using Algorithm~\ref{alg:mle}. Highlighted cells show where the likelihood was improved (AIC reduced) using our algorithm.}

@@

ggplot(all_roots, aes(x = real, y = im, col = mod, pch = mod)) +
  annotate("path", x = cos(seq(0, 2*pi, length.out = 100)),
           y = sin(seq(0, 2*pi, length.out = 100))) +
  geom_hline(yintercept = 0, linewidth = 0.3) +
  geom_vline(xintercept = 0, linewidth = 0.3) +
  geom_point(aes(size = mod), stroke = 1.2) +
  facet_wrap(
    ~type,
    nrow = 1,
    labeller = as_labeller(
      c("AR" = "Inverse AR roots", "MA" = "Inverse MA roots"))
  ) +
  coord_fixed() +
  labs(
    color = NULL, pch = NULL, stroke = NULL, size = NULL, y = 'Imaginary', x = 'Real'
    ) +
  theme_bw() +
  theme(axis.title = ggplot2::element_text(face="bold"),
        legend.position = 'bottom') +
  scale_shape_manual(values = c(1, 4, 3)) +
  scale_size_manual(values = c(3.7, 2.7, 2.7)) +
  scale_color_brewer(palette = 'Dark2')
@
\caption[ARMA polynomial roots]{\label{fig:huronRoots}Inverted AR and MA polynomial roots to the fitted $\text{AR}(1)$ and $\text{ARMA}(2, 1)$ models to the Lake Michigan-Huron data using a single parameter initialization.}
\end{figure}

>>>>

\begin{figure}[ht]
<<mutliMode-fig, fig.height=3.5, fig.width=7>>=
ggpubr::ggarrange(
  plotlist = ggs,
  legend = 'right',
  common.legend = TRUE
)
@
\caption[The profile log-likelihood of data simulated from four distinct MA(1) models.]{\label{fig:multiMode}The profile log-likelihood of data simulated from four distinct MA(1) models. The solid, black line indicates the true value of $\theta_1$; the dotted line is the CSS-initialization. The dashed lines correspond to the estimate $\hat{\theta}_1$ using \code{stats:arima} (red) and our proposed algorithm (implemented in \code{arima2::arima}, blue).}
\end{figure}

@@

\begin{figure}[!ht]
<<simProps, fig.height=3, fig.width=4.5>>=
wide_res %>%
  filter(P != 0 & Q !=0) %>%
  group_by(P, Q, n) %>%
  summarize(pct_improve = sum(ll_arima2 > ll_arima, na.rm = TRUE) / n()) %>%
  ggplot(aes(x = n, y = pct_improve)) +
  facet_grid(Q~P, labeller = labeller(P = AR_labs, Q = MA_labs)) +
  geom_line() +
  geom_point() +
  scale_y_continuous(limits = c(0, 0.6)) +
  ylab("Proportion of Improved Fits") +
  xlab("Number of observations (n)")
@
\caption[Proportion of simulated data with improved likelihood from using multiple restarts (Algorithm~\ref{alg:mle}).]{\label{fig:simProps}Proportion of simulated data with improved likelihood from using multiple restarts (Algorithm~\ref{alg:mle}).}
\end{figure}

@@

ggpubr::ggarrange(
  gg_fisher, gg_profile, align = 'h', nrow = 1,
  labels = 'AUTO',
  label.x = c(0.16, 0)
)
@
\caption[Proportion of models that achieved nominal coverage of Bonferroni adjusted $95\%$ confidence intervals.]{\label{fig:pctCovered}Proportion of models that achieved nominal coverage of Bonferroni adjusted $95\%$ confidence intervals. The dashed line denotes the target coverage level. (A) Confidence intervals created using Fisher's information matrix. (B) Confidence intervals created using profile likelihoods.}
\end{figure}

@@

simTables %>%
  group_by(n, P, Q, max_repeat) %>%
  summarize(
    pct_consistent = sum(consistent, na.rm = TRUE) / sum(!is.na(consistent))
  ) %>%
  ggplot(
    aes(
      x = n, y = pct_consistent,
      group = as.factor(max_repeat),
      color = as.factor(max_repeat),
      linetype = as.factor(max_repeat)
    )
  ) +
  geom_line() +
  geom_point() +
  facet_grid(P~Q, labeller = labeller(P = AR_labs, Q = MA_labs)) +
  ylab("Proportion of Tables\n that are Consistent") +
  xlab("Number of observations") +
  theme(legend.title = element_blank(), legend.position = 'bottom') +
  scale_color_discrete(labels = restart_labels) +
  scale_linetype_discrete(labels = restart_labels) +
  scale_y_continuous(limits = c(0.35, 1))
@
\caption[Proportion of consistent AIC tables.]{\label{fig:AICtabRes}Proportion of consistent AIC tables. Data is generated from ARMA$(p, q)$ models with $(p, q) \in \{1, 2, 3\}^2$, and the corresponding AIC table is created. The Y-axis shows the percentage of tables that were consistent. M is the number of times a maxima is observed before the algorithm terminates, so $M=1$ corresponds to the standard maximization procedure.}
\end{figure}

@@

    \caption[AIC values of ARMA models fit to Lake Michigan-Huron depths.]{\label{tab:huronTab}AIC values of ARMA models fit to Lake Michigan-Huron depths. Table~\ref{tab:AIC1} was computing using only a single parameter initialization. Table~\ref{tab:AIC2} was computed using Algorithm~\ref{alg:mle}. Highlighted cells show where the likelihood was improved (AIC reduced) using our algorithm.}

@@

ggplot(all_roots, aes(x = real, y = im, col = mod, pch = mod)) +
  annotate("path", x = cos(seq(0, 2*pi, length.out = 100)),
           y = sin(seq(0, 2*pi, length.out = 100))) +
  geom_hline(yintercept = 0, linewidth = 0.3) +
  geom_vline(xintercept = 0, linewidth = 0.3) +
  geom_point(aes(size = mod), stroke = 1.2) +
  facet_wrap(
    ~type,
    nrow = 1,
    labeller = as_labeller(
      c("AR" = "Inverse AR roots", "MA" = "Inverse MA roots"))
  ) +
  coord_fixed() +
  labs(
    color = NULL, pch = NULL, stroke = NULL, size = NULL, y = 'Imaginary', x = 'Real'
    ) +
  theme_bw() +
  theme(axis.title = ggplot2::element_text(face="bold"),
        legend.position = 'bottom') +
  scale_shape_manual(values = c(1, 4, 3)) +
  scale_size_manual(values = c(3.7, 2.7, 2.7)) +
  scale_color_brewer(palette = 'Dark2')
@
\caption[Inverted polynomial roots of ARMA models.]{\label{fig:huronRoots}Inverted polynomial roots of ARMA models. AR and MA polynomial roots to the fitted $\text{AR}(1)$ and $\text{ARMA}(2, 1)$ models to the Lake Michigan-Huron data using a single parameter initialization.}
\end{figure}

### 2025-05-16 chapters/conclusion/conclusion.tex
Fixing pre-defense review: "All figure and table captions must match word for word up to the first punctuation mark."

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\linewidth]{chapters/conclusion/nestedDesign.pdf}
    \caption{A diagram of a controlled experiment with replications. Each circle represents a unique replicate with its own distinct features. The rectangular boxes represent different treatments, each containing shared features for their respective replications. The entire experiment is encased in a larger rectangle indicating features common across all treatments.}
    \label{fig:controlled_experiment}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\linewidth]{chapters/conclusion/nestedDesign.pdf}
    \caption[A diagram of a controlled experiment with replications.]{A diagram of a controlled experiment with replications. Each circle represents a unique replicate with its own distinct features (parameters). The rectangular boxes represent different treatments, each containing shared features for their respective replications. The entire experiment is encased in a larger rectangle indicating features common across all treatments.}
    \label{fig:controlled_experiment}
\end{figure}
